Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
edited contributions

We describe and evaluate two approaches for synthesising digital controllers
for state-space physical plants, both based on CounterExample
Guided Inductive Synthesis (CEGIS)~\cite{sketch}.
The first approach uses a naive
technique that starts by devising a digital controller that stabilizes the system
whilst remaining safe for a 
pre-selected time horizon; then, it verifies its potential safety by unfolding
the dynamics of the system and checking for a completeness threshold.
As it requires explicit unfolding up to a completeness
threshold, this approach may result in a state space explosion.
Instead of explicitly unfolding the dynamics, the second approach 
employs abstract acceleration~\cite{cattaruzza2015unbounded} to implicitly
evaluate all possible progressions of the system simultaneously.
Additionally, the second approach uses
abstraction refinement enabling us to always start with a very simple description
regardless of the complexity of the overall dynamics, and only expand to more
complex models when a solution cannot be found.

@@

\begin{enumerate}
%
\item In this paper we extend the problem of digital control synthesis from a transfer function representation into a state space representation.
This entails the verification of safety properties in addition to the already existing stability conditions which is a much harder problem.
%
\item To achieve this, we develop two approaches and compare them, the first relying on a non-deterministic simulation of the system and a completeness proof, whilst the second leverages on the concepts of abstraction and acceleration to increase speed whilst retaining soundness.
%
\item We develop a solution generalization algorithm for the first approach and an abstraction refinement for the second, both of which improve the performance of the CEGIS loop. 
%
\item We develop a model for different sources quantization and their effect on the state space progression, for which we find safe bounds that ensure the safety of our controllers in a hybrid continuous-digital domain.
%
\end{enumerate}

>>>>

We describe and evaluate two approaches for synthesising digital controllers
for state-space physical plants, both based on CounterExample
Guided Inductive Synthesis (CEGIS)~\cite{sketch}.
{\em The first approach} uses a naive
technique that starts by devising a digital controller that stabilizes the system
whilst remaining safe for a 
pre-selected time horizon; then, it verifies its potential safety by unfolding
the dynamics of the system and checking for a completeness threshold.
As it requires explicit unfolding up to a completeness
threshold, this approach may result in a state space explosion.
Instead of explicitly unfolding the dynamics, {\em the second approach} 
employs abstract acceleration~\cite{cattaruzza2015unbounded} to implicitly
evaluate all possible progressions of the system simultaneously.
Additionally, the second approach uses
abstraction refinement enabling us to always start with a very simple description
regardless of the complexity of the overall dynamics, and only expand to more
complex models when a solution cannot be found.

@@

\begin{enumerate}
%
\item In this paper we extend the problem of digital control synthesis
  from a transfer function representation into a state space
  representation.  This entails the verification of safety properties
  in addition to the already existing stability conditions which is a
  much harder problem.
%
\item We develop two approaches: the first, naive one relies on
  explicit unfolding of the system's dynamics up to a completeness
  threshold, whilst the second one is abstraction-based and leverages
  on the concept of abstraction refinement and acceleration to increase speed whilst retaining
  soundness.
%
\item We develop a model for different sources quantization and their
  effect on the state space progression, for which we find safe bounds
  that ensure the safety of our controllers in a hybrid
  continuous-digital domain.
%
\end{enumerate}
